---
output: html_document
title: "HHL IEEE Jeff: Take 2"
author: Jeff
date: May 12, 2020
classoption: fleqn
header-includes:
- \setlength{\mathindent}{0pt}
- \setlength\parindent{0pt}
---

### Background

Speech Reception Thresholds (in noise) using IEEE sentences. 

Two groups: 

- young adults without much noise exposure history
- middle-aged adults with quite a bit of noise exposure history

Four conditions (2x2): 

- two stimulus levels (40 and 80 dB SPL)
- either both the target and background noise were diotic (N~0~S~0~), or the target signal was inverted in polarity in one ear (N~0~S~$\pi$~) leading to a phase disparity across the ears

```{r results = 'hide', echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, eval=TRUE}
# Required packages
Pkgs <- c("tidyverse", "brms", "rstan", 
          "tidybayes","bayesplot", "modelr", 
          "parallel", "GGally","here")

# Load packages
lapply(Pkgs, require, c = T)

## Set computing options
ncores = detectCores()
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
#source(here("analysis/goHHL.R"))
```

### The data

uLevs = mean SNR (i.e. SRT) <br />
sdLevs = standard deviation SNR

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# read in data
IEEE_Read <- read.csv(here("IEEEsummaries.csv"), 
                stringsAsFactors = TRUE,  # To cover change in default (FALSE) in R 4.0
                header = TRUE)

# Create data frame/tibble for analysis
IEEE_Data <-
  IEEE_Read %>%
  mutate(dBSPL = factor(dBSPL), # specify dBSPL as a factor (discrete)
         Condition = factor(manipulation, 
                            levels = c("none", "inverted"),
                            labels = c("None", "Inverted")),
         Group = fct_rev(factor(paste0(substr(listener,1,1)))))  %>% # create group variable
  select(Listener = listener, 
         Group, 
         dBSPL, 
         Condition,
         uLevs, 
         sdLevs)

head(IEEE_Data)
```

Check cross tabs for trials by subjects across condition

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
#How many trials per subject per condition?
xtabs(~ Listener + 
        Group +
        Condition +
        dBSPL,
      data = IEEE_Data) 
```

Have a look at the data

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# plot SRTs
Group.labs <- c("Young", "Middle Aged")
names(Group.labs) <- c("Y", "M")

IEEE_Data %>%
  ggplot(aes(x = Condition, y = uLevs, colour = dBSPL)) +
  facet_grid(. ~ Group, 
             labeller = labeller(group = Group.labs)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(size = 3, alpha = 0.2, position = position_jitterdodge()) +
  ylim(-14,3) +
  theme_bw() +
  scale_fill_manual(values=c("#00CC99","#CC0066")) +
  labs(x="", y = "SRT (dB)")+
  scale_x_discrete(labels=c("inverted" = expression("N"[0]*"S"[pi]), "none" = expression("N"[0]*"S"[0]))) + 
  guides(colour=guide_legend(title="Level (dB SPL)")) + 
  theme(
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black"),
    strip.text.x = element_text(size = 12),
    strip.background = element_blank(),
    legend.position = c(0.87, 0.2),
    legend.background = element_rect(fill = "transparent")
  )
```

### Bayesian analysis

We'll build three models with increasing complexity and then compare model fits using a "leave one out" (loo) cross-validation approach

#### Model 1: Intercept-only model

Specify the model as follows: 

$\begin{aligned}
SRT &\sim \mathbf{N}(\mu, \sigma) \\
\mu &= \alpha_{Listener} \\
\alpha_{Listener} &\sim \mathbf{N}(\overline{\alpha}, \sigma_{\alpha}) \\
\overline{\alpha} &\sim \mathbf{N}(-5,1.5) \\
\sigma_{\alpha} &\sim \mathbf{cauchy}(0,1) \\
\sigma &\sim \mathbf{cauchy}(0,1) \\
\end{aligned}$

```{r, eval = FALSE, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
# specify varying intercept & manipulation effect model
SRT_int_only_fmla <- bf(
  uLevs ~ (1 | Listener))

## Get priors from BRMS
SRT_int_only_prior_list <-
  get_prior(SRT_int_only_fmla,
            IEEE_Data,
            family = "gaussian")

# specify priors
int_only_priors <- c(
  set_prior("normal(-5,1.5)",  
            class = "Intercept"),
  set_prior("cauchy(0,1)",  
            class = "sd", 
            coef = "Intercept", 
            group = "Listener"),
  set_prior("normal(0,10)", 
            class = "sigma")
)

# compile and run model
SRT_Int_Only_Mod <- brm(
  SRT_int_only_fmla,
  IEEE_Data,
  family = "gaussian",
  prior = int_only_priors,
  inits = 0,
  iter = 2000,
  warmup = 1000,
  chains = 2,
  cores = ncores,
  sample_prior = TRUE,
  seed = 42,
  control = list(max_treedepth = 12,
                 adapt_delta = 0.9)
)

```

```{r, echo = FALSE, eval = FALSE}
## Save model
save(SRT_int_only_Mod, file = here("SRT_Int_Only_Mod.RDATA"))
```

```{r, echo = FALSE, eval = TRUE}
load(here("SRT_Int_Only_Mod.RDATA"))
summary(SRT_Int_Only_Mod)
```

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
## Plot loo of intercept only model
pp_check(SRT_Int_Only_Mod, 
         type = "loo_pit_overlay")
```

#### Model 2: Add in predictors:

* Manipulation: the effect of inverting the polarity of the speech across the ears. The difference between the two conditions (inverted and not inverted) is the binaural intelligibility level difference (BILD)
* dBSPL: the stimulus level (40 or 80 dB SPL)
* Group: young or middle-aged

Create an index variable for the 'manipulation' variable, where 'none' (i.e. not inverted) = 1, and 'inverted' = 2.  

We will need to come up with a better estimate for the prior, based on the literature, but for now I'll just assume an effect of 'manipulation' (i.e. BILD) of 3 dB with a standard deviation of 1 dB. Since 1 = none, and inverted = 2, I will use a negative mean, because SRTs are expected to decrease (i.e. improve) when the polarity of the speech is inverted in one ear. 

I enter manipulation, Group, and dBSPL as factors, which will automatically be dummuy coded by brms.

Specify the model as follows: 

$\begin{aligned}
SRT_i &\sim \mathbf{N}(\mu, \sigma) \\
\mu_i &= \alpha_{Listener_i} + \beta_{M_i} * manipulation_i + \beta_{dBSPL_i} * dBSPL_i + \beta_{G_i} * Group_i \\
\alpha_{Listener} &\sim \mathbf{N}(\overline{\alpha}, \sigma_{\alpha}) \\
\overline{\alpha} &\sim \mathbf{N}(-5,1.5) \\
\sigma_{\alpha} &\sim \mathbf{cauchy}(0,1) \\
\beta_{M} &\sim \mathbf{N}(-3, 1) \\
\beta_{dBSPL} &\sim N(-3, 1) \\
\beta_{G} &\sim \mathbf{N}(1, 1) \\
\sigma &\sim \mathbf{cauchy}(0,1) \\
\end{aligned}$

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, eval = FALSE}
# specify varying intercept & manipulation effect model
SRT_Int_fmla <- bf(
  uLevs ~ Condition + 
    Group +
    dBSPL +
    (1 | Listener))

## Get priors from BRMS
SRT_Int_prior_list <-
  get_prior(SRT_Int_fmla,
            IEEE_Data,
            family = "gaussian")

# specify priors
int_priors <- c(
  set_prior("normal(-5,1.5)",  
            class = "Intercept"),
  set_prior("normal(-3,1)", 
            class = "b", 
            coef = "ConditionInverted"),
  set_prior("normal(-3,1)",  
            class = "b", 
            coef = "dBSPL80"),
  set_prior("normal(1,1)",  
            class = "b", 
            coef = "GroupM"),
  set_prior("cauchy(0,1)", 
            class = "sd"),
  set_prior("cauchy(0,1)",  
            class = "sd", 
            coef = "Intercept", 
            group = "Listener"),
  set_prior("normal(0,10)", 
            class = "sigma")
)

# compile and run model
SRT_Int_Mod <- brm(
  SRT_Int_fmla,
  IEEE_Data,
  family = "gaussian",
  prior = int_priors,
  inits = 0,
  iter = 2000,
  warmup = 1000,
  chains = 2,
  cores = ncores,
  sample_prior = TRUE,
  seed = 42,
  control = list(max_treedepth = 12,
                 adapt_delta = 0.9)
)
```

```{r, eval = FALSE}
save(SRT_Int_Mod, file = here("SRT_Int_Mod.RDATA"))
```

```{r, echo = FALSE, eval = TRUE}
load(here("SRT_Int_Mod.RDATA"))
summary(SRT_Int_Mod)
```

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
## Plot loo of varyng intercept model
pp_check(SRT_Int_Mod, 
         type = "loo_pit_overlay")
```

#### Model 3: Add a varying slope for dBSPL to estimate differences between stimulus level across participants

Specify the model as follows: 

$\begin{aligned}
SRT_{i} &\sim \mathbf{N}(\mu, \sigma) \\
\mu_{i} &= \alpha_{Listener_i} + \beta_{M_i} * manipulation_i + \beta_{dBSPL_i} * dBSPL_i + \beta_{G_i} * Group_i \\
\alpha_{Listener} &\sim \mathbf{N}(\overline{\alpha}, \sigma_{\alpha} \\
\overline{\alpha} &\sim \mathbf{N}(-5,1.5) \\
\sigma_{\alpha} &\sim \mathbf{cauchy}(0,1) \\
\beta_{M} &\sim \mathbf{N}(-3, 1) \\
\beta_{dBSPL} &\sim \mathbf{N}(-3, 1) \\
\beta_{G} &\sim \mathbf{N}(1, 1) \\
\sigma &\sim \mathbf{cauchy}(0,1) \\
\left[\begin{array}
{r}
\alpha_{Listener}  \\
\beta_{Listener}
\end{array}\right] &\sim
\mathbf{MVNormal}\left( \left[\begin{array}
{r}
\alpha  \\
\beta
\end{array}\right], \mathbf{S} \right) \\
\mathbf{S} &= \left[\begin{array}
{rr}
\sigma_{\alpha}^{2} & 0  \\
0 & \sigma_{\beta}^{2}
\end{array}\right] 
\mathbf{R} \left[\begin{array}
{rr}
\sigma_{\alpha}^{2} & 0  \\
0 & \sigma_{\beta}^{2}
\end{array}\right] \\
\mathbf{R} &\sim~ lkj(1) 
\end{aligned}$

```{r, eval = FALSE}
# specify varying intercept,slope, & manipulation effect model
SRT_Int_Slope_fmla <- bf(
  uLevs ~ Condition + 
    Group +
    dBSPL +
    (dBSPL | Listener))

## Get priors from BRMS
SRT_Int_Slope_prior_list <-
  get_prior(SRT_Int_Slope_fmla,
            IEEE_Data,
            family = "gaussian")

# specify priors
int_slope_priors <- c(
  set_prior("normal(-5,1.5)",  
            class = "Intercept"),
  set_prior("normal(-3,1)", 
            class = "b", 
            coef = "ConditionInverted"),
  set_prior("normal(-3,1)",  
            class = "b", 
            coef = "dBSPL80"),
  set_prior("normal(1,1)",  
            class = "b", 
            coef = "GroupM"),
  set_prior("cauchy(0,1)", 
            class = "sd"),
  set_prior("cauchy(0,1)",  
            class = "sd", 
            coef = "Intercept", 
            group = "Listener"),
  set_prior("cauchy(0,1)",  
            class = "sd", 
            coef = "dBSPL80", 
            group = "Listener"),
  set_prior("normal(0,10)", 
            class = "sigma"),
  set_prior("lkj(1)", 
            class = "cor")
)

# compile and run model
SRT_Int_Slope_Mod <- brm(
  SRT_Int_Slope_fmla,
  IEEE_Data,
  family = "gaussian",
  prior = int_slope_priors,
  inits = 0,
  iter = 2000,
  warmup = 1000,
  chains = 2,
  cores = ncores,
  sample_prior = TRUE,
  seed = 42,
  control = list(max_treedepth = 12,
                 adapt_delta = 0.9)
)
```

```{r, eval = FALSE}
# Save model
save(SRT_Int_Slope_Mod, file = here("SRT_Int_Slope_Mod.RDATA"))
```

```{r, echo = FALSE, eval = TRUE}
load(here("SRT_Int_Slope_Mod.RDATA"))
summary(SRT_Int_Slope_Mod)
```

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
## Plot loo of varying intercept and slope model
pp_check(SRT_Int_Slope_Mod, 
         type = "loo_pit_overlay")
```

#### Model 4: Add interaction terms for manipulation by Group and dBSPL by Group, as well as the varying slopes and intercepts

Specify the model as follows: 

$\begin{aligned}
SRT_{i} &\sim \mathbf{N}(\mu, \sigma) \\
\mu_{i} &= \alpha_{Listener_i} + \beta_{M_i} * manipulation_i + \beta_{dBSPL_i} * dBSPL_i + \beta_{G_i} * Group_i + \beta_{MG_i} * manipulation:Group_i + \beta_{dBG_i} * dBSPL:Group_i \\
\alpha_{Listener} &\sim \mathbf{N}(\overline{\alpha}, \sigma_{\alpha} \\
\overline{\alpha} &\sim \mathbf{N}(-5,1.5) \\
\sigma_{\alpha} &\sim \mathbf{cauchy}(0,1) \\
\beta_{M} &\sim \mathbf{N}(-3, 1) \\
\beta_{dBSPL} &\sim \mathbf{N}(-3, 1) \\
\beta_{G} &\sim \mathbf{N}(1, 1) \\
\beta_{MG} &\sim \mathbf{N}(1, 1) \\
\beta_{dBG} &\sim \mathbf{N}(1, 1) \\
\sigma &\sim \mathbf{cauchy}(0,1) \\
\left[\begin{array}
{r}
\alpha_{Listener}  \\
\beta_{Listener}
\end{array}\right] &\sim
\mathbf{MVNormal}\left( \left[\begin{array}
{r}
\alpha  \\
\beta
\end{array}\right], \mathbf{S} \right) \\
\mathbf{S} &= \left[\begin{array}
{rr}
\sigma_{\alpha}^{2} & 0  \\
0 & \sigma_{\beta}^{2}
\end{array}\right] 
\mathbf{R} \left[\begin{array}
{rr}
\sigma_{\alpha}^{2} & 0  \\
0 & \sigma_{\beta}^{2}
\end{array}\right] \\
\mathbf{R} &\sim~ lkj(1) 
\end{aligned}$

```{r, eval = FALSE}
# specify interaction terms as well as varying intercept,slope, & manipulation effect model
SRT_Full_fmla <- bf(
  uLevs ~ Condition + 
    Group +
    dBSPL +
    Condition:Group +
    dBSPL:Group +
    (dBSPL | Listener))

## Get priors from BRMS
SRT_Full_prior_list <-
  get_prior(SRT_Full_fmla,
            IEEE_Data,
            family = "gaussian")

# specify priors
full_priors <- c(
  set_prior("normal(-5,1.5)",  
            class = "Intercept"),
  set_prior("normal(-3,1)", 
            class = "b", 
            coef = "ConditionInverted"),
  set_prior("normal(-3,1)",  
            class = "b", 
            coef = "dBSPL80"),
  set_prior("normal(1,1)",  
            class = "b", 
            coef = "GroupM"),
  set_prior("normal(0,8)",  # These are pretty wide as guesses
            class = "b", 
            coef = "ConditionInverted:GroupM"),
  set_prior("normal(0,8)",  
            class = "b", 
            coef = "GroupM:dBSPL80"),
  set_prior("cauchy(0,1)", 
            class = "sd"),
  set_prior("cauchy(0,1)",  
            class = "sd", 
            coef = "Intercept", 
            group = "Listener"),
  set_prior("cauchy(0,1)",  
            class = "sd", 
            coef = "dBSPL80", 
            group = "Listener"),
  set_prior("normal(0,10)", 
            class = "sigma"),
  set_prior("lkj(1)", 
            class = "cor")
)

# compile and run model
SRT_Full_Mod <- brm(
  SRT_Full_fmla,
  IEEE_Data,
  family = "gaussian",
  prior = full_priors,
  inits = 0,
  iter = 2000,
  warmup = 1000,
  chains = 2,
  cores = ncores,
  sample_prior = TRUE,
  seed = 42,
  control = list(max_treedepth = 12,
                 adapt_delta = 0.9)
)
```

```{r, eval = FALSE}
# Save model
save(SRT_Full_Mod, file = here("SRT_Full_Mod.RDATA"))
```

```{r, echo = FALSE, eval = TRUE}
load(here("SRT_Full_Mod.RDATA"))
summary(SRT_Full_Mod)
```

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
## Plot loo of final model
pp_check(SRT_Full_Mod, 
         type = "loo_pit_overlay")
```

#### Compare model fits using loo
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
loo(SRT_Int_Only_Mod, 
    SRT_Int_Mod, 
    SRT_Int_Slope_Mod,
    SRT_Full_Mod, 
    reloo = TRUE)

## Alternate way to present only what we need
# Add loo criterion for each model
Int_Only_loo <- add_criterion(SRT_Int_Only_Mod,
                              criterion = c("loo","bayes_R2"), 
                              reloo = TRUE)
Int_loo <- add_criterion(SRT_Int_Mod,
                         criterion = c("loo","bayes_R2"), 
                         reloo = TRUE)
Int_Slope_loo <- add_criterion(SRT_Int_Slope_Mod,
                               criterion = c("loo","bayes_R2"), 
                               reloo = TRUE)
Full_loo <- add_criterion(SRT_Full_Mod,
                          criterion = c("loo","bayes_R2"), 
                          reloo = TRUE)
# Compare models
loo_compare(Int_Only_loo,
            Int_loo,
            Int_Slope_loo,
            Full_loo)

##Compare models using leave one out (loo) weights
model_weights(SRT_Int_Only_Mod, 
               SRT_Int_Mod, 
               SRT_Int_Slope_Mod,
               SRT_Full_Mod, 
              weights = "loo")
```

It doesn't look like the interactions add much to the fit, so we could go with the more parsimonious solution - varying intercepts and slopes, but no interaction terms

#### Visualizations of "final" model, which has varying intercepts and slopes, but no interaction terms

We can start with a "conventional" dot plot of predicted means and 95% credible intervals:

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
point_interval(
  .data = IEEE_Data %>%
    data_grid(Condition, Group, dBSPL) %>%
    add_fitted_draws(
      SRT_Int_Slope_Mod,
      n = 30,
      allow_new_levels = TRUE,
      re_formula = NULL
    ),
  .width = 0.89,
  .point = median,
  .interval = hdci,
  .simple_names = TRUE,
  na.rm = FALSE,
  .exclude = c(".chain", ".iteration", ".draw", ".row")
) %>%

ggplot(aes(dBSPL, .value, shape = Condition)) +
  geom_point(position = position_dodge(width = 0.4), size = 3) +
  facet_wrap(~ Group) +
  geom_errorbar(aes(ymin = .lower, ymax = .upper),
                width = 0.3,
                position = position_dodge(width = 0.4)) +
  scale_y_continuous("uLev") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5),
    plot.title = element_text(hjust = 0.5),
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black"),
    strip.text.x = element_text(size = 12),
    strip.background = element_blank()
  )

```

Then we can build this out to show the predted means, 95 and 68% credible intervals as well as the distributions of posterior predictions from the model:

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
## Predictions with distributions
IEEE_Data %>%
  data_grid(Condition, Group, dBSPL) %>%
  add_fitted_draws(
    SRT_Int_Slope_Mod,
    n = 100,
    allow_new_levels = TRUE,
    re_formula = NULL
  )  %>%
  
  ggplot(aes(dBSPL, .value)) +
  #geom_point(position = position_dodge(width = 0.4), size = 3) +
  facet_grid(Condition ~ Group) +
  stat_eye() +
  #coord_flip() +
  scale_y_continuous("dB SNR",) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5),
    plot.title = element_text(hjust = 0.5),
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black"),
    strip.text.x = element_text(size = 12),
    strip.background = element_blank()
  )
```

A a Kruschke-style plot showing both the predictive uncertainty and the parameter uncertainty simultaneously by showing several possible predictive distributions implied by the posterior:

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
IEEE_Data %>%
  data_grid(Listener, Condition, Group, dBSPL) %>%
  add_fitted_draws(SRT_Int_Slope_Mod, dpar = c("mu", "sigma")) %>%
  sample_draws(30) %>%
  ggplot(aes(y = Group)) +
  facet_wrap(~ Condition) +
  stat_dist_slabh(aes(dist = "norm", arg1 = mu, arg2 = sigma), 
                  slab_color = "gray65", alpha = 1/10, fill = NA
  ) +
  geom_point(aes(x = uLevs), 
             data = IEEE_Data, 
             shape = 21, 
             fill = "#9ECAE1", 
             size = 2) +
  scale_x_continuous("uLevs") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5),
    plot.title = element_text(hjust = 0.5),
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.line = element_line(colour = "black"),
    strip.text.x = element_text(size = 12),
    strip.background = element_blank()
  )

```

Return the varibles in the model:

```{r, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
get_variables(SRT_Int_Slope_Mod)
```

We can build out plots of the posterior using tidybayes:

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
## Posterior intervals with densities
SRT_Int_Slope_Mod %>%
  spread_draws(b_Intercept, 
               b_ConditionInverted,
               b_GroupM,
               b_dBSPL80,
               r_Listener[GroupListener, Term] | Term,
  ) %>%
  ungroup() %>%
  
  mutate(None_Y_dBSPL40 = b_Intercept + 
           Intercept,
         
         Inverted_Y_dBSPL40 = b_Intercept +
           b_ConditionInverted +
           Intercept,
         
         None_M_dBSPL40 = b_Intercept +
           b_GroupM +
           Intercept,
         
         Inverted_M_dBSPL40 = b_Intercept +
           b_GroupM +
           b_ConditionInverted +
           Intercept,
         
         None_Y_dBSPL80 = b_Intercept +
           b_dBSPL80 +
           Intercept +
           dBSPL80,
         
         Inverted_Y_dBSPL80 = b_Intercept +
           b_ConditionInverted +
           b_dBSPL80 +
           Intercept +
           dBSPL80,
         
         None_M_dBSPL80 = b_Intercept +
           b_GroupM +
           b_dBSPL80 +
           Intercept +
           dBSPL80,
         
         Inverted_M_dBSPL80 = b_Intercept +
           b_GroupM +
           b_ConditionInverted +
           b_dBSPL80 +
           Intercept +
           dBSPL80 
  ) %>%
  select(.chain:.draw, GroupListener, None_Y_dBSPL40:Inverted_M_dBSPL80) %>%
  pivot_longer(cols = None_Y_dBSPL40:Inverted_M_dBSPL80, 
               names_to = "Case", 
               values_to = "Post_Mean") %>%
  separate(Case, into = c("Condition", "Group2", "Level")) %>%
  separate(GroupListener, c("Group", "Listener"), sep = 1) %>%
  filter(Group == Group2) %>% 
  select(-Group2) %>%
  mutate(Group = factor(Group, levels = c("Y", "M")), 
         Listener = factor(Listener),
         Level = factor(Level, levels = c("dBSPL40", "dBSPL80")),
         Condition = factor(Condition, levels = c("None", "Inverted")),
         Post_Odds = exp(Post_Mean),
         Post_Prob = Post_Odds/(1 + Post_Odds)) %>%
  select(-Listener) %>%
  group_by(.chain, .iteration, .draw, Group, Condition, Level) %>%
  summarize_all(mean) %>%
  
  ggplot(aes(y = Level, x = Post_Mean)) +
  facet_grid(Group ~ Condition) +
  stat_halfeyeh() +
  scale_y_discrete("Condition") +
  scale_x_continuous("Posterior Estimate") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5), 
        plot.title = element_text(hjust = 0.5),
        panel.border=element_rect(fill=NA,colour="black"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        strip.text.x=element_text(size=12),strip.background = element_blank())
```

We can also look at densities of differnces between conditions:

```{r, echo=TRUE, warning=FALSE, error=FALSE, message=FALSE, eval = TRUE}
SRT_Int_Slope_Mod %>%
  spread_draws(b_Intercept, 
               b_ConditionInverted,
               b_GroupM,
               b_dBSPL80,
               r_Listener[GroupListener, Term] | Term,
  ) %>%
  ungroup() %>%
  
  mutate(None_Y_dBSPL40 = b_Intercept + 
           Intercept,
         
         Inverted_Y_dBSPL40 = b_Intercept +
           b_ConditionInverted +
           Intercept,
         
         None_M_dBSPL40 = b_Intercept +
           b_GroupM +
           Intercept,
         
         Inverted_M_dBSPL40 = b_Intercept +
           b_GroupM +
           b_ConditionInverted +
           Intercept,
         
         None_Y_dBSPL80 = b_Intercept +
           b_dBSPL80 +
           Intercept +
           dBSPL80,
         
         Inverted_Y_dBSPL80 = b_Intercept +
           b_ConditionInverted +
           b_dBSPL80 +
           Intercept +
           dBSPL80,
         
         None_M_dBSPL80 = b_Intercept +
           b_GroupM +
           b_dBSPL80 +
           Intercept +
           dBSPL80,
         
         Inverted_M_dBSPL80 = b_Intercept +
           b_GroupM +
           b_ConditionInverted +
           b_dBSPL80 +
           Intercept +
           dBSPL80 
  ) %>%
  select(.chain:.draw, GroupListener, None_Y_dBSPL40:Inverted_M_dBSPL80) %>%
  pivot_longer(cols = None_Y_dBSPL40:Inverted_M_dBSPL80, 
               names_to = "Case", 
               values_to = "Post_Mean") %>%
  separate(Case, into = c("Condition", "Group2", "Level")) %>%
  separate(GroupListener, c("Group", "Listener"), sep = 1) %>%
  filter(Group == Group2) %>% 
  select(-Group2) %>%
  mutate(Group = factor(Group, levels = c("Y", "M")), 
         Listener = factor(Listener),
         Level = factor(Level, levels = c("dBSPL40", "dBSPL80")),
         Condition = factor(Condition, levels = c("None", "Inverted")),
         Post_Odds = exp(Post_Mean),
         Post_Prob = Post_Odds/(1 + Post_Odds)) %>%
  select(-Listener) %>%
  group_by(.chain, .iteration, .draw, Group, Condition, Level) %>%
  summarize_all(mean) %>%
  ungroup() %>%
  group_by(Level, Condition) %>%
  compare_levels(Post_Mean, 
                 by = Group) %>% 
 
  ggplot(aes(y = Group, x = Post_Mean)) +
  facet_grid(Level ~ Condition) +
  stat_halfeyeh() +
  scale_x_continuous("Posterior Mean Difference") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5), plot.title = element_text(hjust = 0.5),
        panel.border=element_rect(fill=NA,colour="black"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        strip.text.x=element_text(size=12),strip.background = element_blank())
```


